# =============================================================================
# Study 3 & 4 Integration Analysis - Complete Code (Matching Original Style)
# =============================================================================

---
title: "Study 3 & 4 Integration Analysis"
author: "Research Team"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
if (!requireNamespace('pacman', quietly = TRUE)) {
    install.packages('pacman')
}

pacman::p_load(
  here, tidyverse, bruceR, boot,
  ggplot2, ggdist, ggridges, patchwork,
  papaja, cowplot, gridExtra,
  metafor, e1071, nortest,
  RColorBrewer
)

options(scipen = 999)
options(warn = -1)

# Color palette (consistent with original code)
COLORS <- c("empirical" = "#a72126", "simulated" = "#12264f")
```

---

# Part 1: Data Preprocessing

## 1.1 Define Group Information
```{r}
# Group mapping for 8 experimental groups
GROUP_INFO <- tribble(
  ~new_groupID, ~source, ~P, ~T, ~W, ~Condition,
  1, "S3+S4", 0, 30, 300, "P=0,T=30,W=300",
  2, "S3+S4", 0, 30, 600, "P=0,T=30,W=600",
  3, "S3+S4", 120, 30, 600, "P=120,T=30,W=600",
  4, "S3+S4", 120, 80, 600, "P=120,T=80,W=600",
  5, "S3+S4", 8, 100, 1100, "P=8,T=100,W=1100",
  6, "S3+S4", 120, 500, 1500, "P=120,T=500,W=1500",
  7, "S4", 120, 30, 800, "P=120,T=30,W=800",
  8, "S4", 120, 80, 800, "P=120,T=80,W=800"
)

CONDITION_ORDER <- c(
  "P=0,T=30,W=300", "P=0,T=30,W=600", "P=120,T=30,W=600",
  "P=120,T=80,W=600", "P=8,T=100,W=1100", "P=120,T=500,W=1500",
  "P=120,T=30,W=800", "P=120,T=80,W=800"
)

# Data type conversion
convert_data_type_emp <- function(df) {
  df <- df %>% 
    dplyr::mutate(
      groupID = as.numeric(groupID),
      subjectID = as.numeric(subjectID),
      gender = as.numeric(gender),
      age = as.numeric(age),
      handedness = as.numeric(handedness),
      stage = as.character(stage),
      trialID = as.numeric(trialID),
      P = as.numeric(P), T = as.numeric(T), W = as.numeric(W),
      Shape = as.character(Shape), Label = as.character(Label),
      CorrectKey = as.character(CorrectKey), Response = as.character(Response),
      RT = as.numeric(RT), Correct = as.numeric(Correct)
    )
  return(df)
}
```

## 1.2 Load Empirical Data
```{r}
file_emp <- list.files(
  here::here("3_Study3&4", "data", "raw", "emp_data"), 
  pattern = "EXP.*\\.csv$", full.names = TRUE)

# Exclude NoMask files
file_emp_main <- file_emp[!grepl("NoMask", file_emp)]

df_emp <- data.frame()
for (i in seq_along(file_emp_main)) {
  df <- read.csv(file_emp_main[i], header = TRUE) %>% convert_data_type_emp()
  df_emp <- dplyr::bind_rows(df_emp, df)
}

message(paste("Empirical data:", nrow(df_emp), "rows"))
message("Subjects per group:")
print(table(df_emp$groupID))
```

## 1.3 Filter and Process
```{r}
df_emp <- df_emp %>%
  filter(stage == "formal") %>%
  mutate(
    MatchKey = case_when(
      subjectID %% 4 == 1 ~ "f",
      subjectID %% 4 == 2 ~ "j",
      subjectID %% 4 == 3 ~ "j",
      subjectID %% 4 == 0 ~ "f",
      TRUE ~ NA_character_
    ),
    Matchness = ifelse(CorrectKey == MatchKey, "match", "mismatch"),
    T_ms = T * 1000, W_ms = W * 1000, RT_ms = RT * 1000,
    Press = ifelse(!is.nan(RT), 1, 0)
  )

# Add Condition labels
df_emp <- df_emp %>%
  left_join(GROUP_INFO %>% select(new_groupID, Condition), 
            by = c("groupID" = "new_groupID"))

# Filter match trials
df_emp_match <- df_emp %>% 
  filter(Matchness == "match") %>%
  mutate(Type = "empirical") %>%
  select(groupID, subjectID, Type, trialID, P, T_ms, W_ms, Label, Press, Correct, RT_ms, Condition)
```

## 1.4 Load Simulated Data
```{r}
file_sim <- list.files(
  here::here("3_Study3&4", "data", "raw", "sim_data"), 
  pattern = "^d.*\\.csv$", full.names = TRUE)

df_sim <- data.frame()
for (i in seq_along(file_sim)) {
  df <- read.csv(file_sim[i], header = TRUE)
  df$groupID <- i
  df_sim <- dplyr::bind_rows(df_sim, df)
}

df_sim <- df_sim %>%
  mutate(
    Type = "simulated",
    RT_ms = RT * 1000,
    T_ms = T, W_ms = W,
    Press = response, Correct = response
  ) %>%
  select(groupID, subjectID, Type, trialID, P, T_ms, W_ms, Label, v, a, Press, Correct, RT_ms) %>%
  left_join(GROUP_INFO %>% select(new_groupID, Condition), 
            by = c("groupID" = "new_groupID"))
```

## 1.5 Combine
```{r}
df_combined <- dplyr::bind_rows(df_emp_match, df_sim) %>%
  mutate(uniqueID = paste(Type, groupID, subjectID, sep = "_"))

# Set Condition order
df_combined$Condition <- factor(df_combined$Condition, levels = CONDITION_ORDER)

bruceR::export(df_combined, file = here::here("3_Study3&4", "data", "processed", "combined_data.csv"))
message("Data preprocessing complete!")
```

---

# Part 2: Descriptive Statistics

## 2.1 Group-Level Summary
```{r}
df_group <- df_combined %>%
  group_by(groupID, Type, Label, Condition) %>%
  summarise(
    n = n(),
    mean_RT = mean(RT_ms, na.rm = TRUE),
    sd_RT = sd(RT_ms, na.rm = TRUE),
    mean_ACC = mean(Correct == 1, na.rm = TRUE),
    sd_ACC = sd(Correct == 1, na.rm = TRUE),
    P = mean(P), T = mean(T_ms), W = mean(W_ms),
    .groups = "drop"
  )
```

## 2.2 Individual-Level Summary
```{r}
df_individual <- df_combined %>%
  group_by(groupID, subjectID, Type, Label, Condition) %>%
  summarise(
    n = n(),
    mean_RT = mean(RT_ms, na.rm = TRUE),
    sd_RT = sd(RT_ms, na.rm = TRUE),
    mean_ACC = mean(Correct == 1, na.rm = TRUE),
    sd_ACC = sd(Correct == 1, na.rm = TRUE),
    .groups = "drop"
  )
```

## 2.3 Cohen's d Calculation
```{r}
df_group_wide <- df_group %>%
  pivot_wider(
    id_cols = c(groupID, Type, Condition),  
    names_from = Label,
    values_from = c(mean_RT, sd_RT, mean_ACC, sd_ACC, n)
  )

df_group_wide <- df_group_wide %>%
  mutate(
    cohen_d_RT = ifelse(!is.na(mean_RT_self) & !is.na(mean_RT_stranger),
      (mean_RT_stranger - mean_RT_self) / sqrt(((n_stranger-1)*sd_RT_stranger^2 + (n_self-1)*sd_RT_self^2)/(n_self+n_stranger-2)), NA),
    cohen_d_ACC = ifelse(!is.na(mean_ACC_self) & !is.na(mean_ACC_stranger),
      (mean_ACC_self - mean_ACC_stranger) / sqrt(((n_self-1)*sd_ACC_self^2 + (n_stranger-1)*sd_ACC_stranger^2)/(n_self+n_stranger-2)), NA)
  )

df_individual_wide <- df_individual %>%
  pivot_wider(
    id_cols = c(groupID, subjectID, Type, Condition),  
    names_from = Label,
    values_from = c(mean_RT, sd_RT, mean_ACC, sd_ACC, n)
  )

df_individual_wide <- df_individual_wide %>%
  mutate(
    cohen_d_RT = ifelse(!is.na(mean_RT_self) & !is.na(mean_RT_stranger),
      (mean_RT_stranger - mean_RT_self) / sqrt(((n_stranger-1)*sd_RT_stranger^2 + (n_self-1)*sd_RT_self^2)/(n_self+n_stranger-2)), NA),
    cohen_d_ACC = ifelse(!is.na(mean_ACC_self) & !is.na(mean_ACC_stranger),
      (mean_ACC_self - mean_ACC_stranger) / sqrt(((n_self-1)*sd_ACC_self^2 + (n_stranger-1)*sd_ACC_stranger^2)/(n_self+n_stranger-2)), NA)
  )

# Filter mask groups (exclude group 7 which is NoMask - not in current data)
df_group_mask <- df_group %>% filter(groupID != 7)
df_group_wide_mask <- df_group_wide %>% filter(groupID != 7)
df_individual_mask <- df_individual %>% filter(groupID != 7)
df_individual_mask_wide <- df_individual_wide %>% filter(groupID != 7)

bruceR::export(df_group_wide, file = here::here("3_Study3&4", "data", "processed", "effect_size_group.csv"))
message("Descriptive complete!")
```

---

# Part 3: RT Analysis (Matching Original Style)

## 3.1 RT by Condition
```{r}
# RT plot with both empirical and simulated
rt_theme <- theme(
  axis.title.x = element_text(size = 20, face = "bold", color = "black"),
  axis.title.y = element_text(size = 20, face = "bold", color = "black"),
  axis.text.x = element_text(size = 19, face = "bold", color = "black"),
  axis.text.y = element_text(size = 19, face = "bold", color = "black"),
  strip.text = element_text(size = 18, face = "bold", color = "black"),
  legend.title = element_text(size = 21, face = "bold", color = "black"),
  legend.text = element_text(size = 20, face = "bold", color = "black")
)

b1 <- ggplot(df_group_mask, 
             aes(x = Label, y = mean_RT, color = Type, shape = Type)) +
  geom_point(size = 3.5, position = position_dodge(0.5)) +
  geom_errorbar(aes(ymin = mean_RT - sd_RT, ymax = mean_RT + sd_RT),
                width = 0.1, position = position_dodge(0.5)) +
  labs(x = "Type", y = "Reaction Time") +
  facet_wrap(~ Condition, nrow = 2) +
  papaja::theme_apa() +
  scale_color_manual(values = COLORS) +
  rt_theme

RT <- b1 +
  geom_jitter(data = df_individual_mask, 
              aes(x = Label, y = mean_RT, color = Type, shape = Type),
              size = 2.5, alpha = 0.3, 
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.5)) +
  labs(x = "Design", y = "RT")

RT
```

## 3.2 Cohen's d RT
```{r}
cd_RT <- ggplot(df_individual_mask_wide, 
                aes(x = Condition, y = cohen_d_RT, color = Type, shape = Type)) +
  geom_boxplot(aes(fill = Type), alpha = 0.2, outlier.shape = NA) +
  geom_jitter(size = 2.5, alpha = 0.5, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75)) +
  labs(x = "Design", y = "cohen's d RT") +
  papaja::theme_apa() +
  scale_color_manual(values = COLORS) +
  scale_fill_manual(values = COLORS) +
  scale_y_continuous(breaks = seq(-1, 1.5, by = 0.2)) +
  rt_theme

cd_RT
```

## 3.3 Save
```{r}
ggsave(here::here("3_Study3&4", "figures", "RT.png"), plot = RT, width = 11, height = 7, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "cd_RT.png"), plot = cd_RT, width = 14, height = 5, dpi = 300)
```

---

# Part 4: ACC Analysis

## 4.1 ACC by Condition
```{r}
b2 <- ggplot(df_group_mask, 
             aes(x = Label, y = mean_ACC, color = Type, shape = Type)) +
  geom_point(size = 3.5, position = position_dodge(0.5)) +
  geom_errorbar(aes(ymin = mean_ACC - sd_ACC, ymax = mean_ACC + sd_ACC),
                width = 0.1, position = position_dodge(0.5)) +
  labs(x = "Matchness", y = "ACC") +
  facet_wrap(~ Condition, nrow = 2) +
  scale_y_continuous(limits = c(0, 1)) +
  papaja::theme_apa() +
  scale_color_manual(values = COLORS) +
  rt_theme

ACC <- b2 +
  geom_jitter(data = df_individual_mask, 
              aes(x = Label, y = mean_ACC, color = Type, shape = Type),
              size = 2.5, alpha = 0.3, 
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.5)) +
  labs(x = "Design", y = "ACC")

ACC
```

## 4.2 Cohen's d ACC
```{r}
cd_ACC <- ggplot(df_individual_mask_wide, 
                 aes(x = Condition, y = cohen_d_ACC, color = Type, shape = Type)) +
  geom_boxplot(aes(fill = Type), alpha = 0.2, outlier.shape = NA) +
  geom_jitter(size = 2.5, alpha = 0.5, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75)) +
  labs(x = "Design", y = "cohen's d ACC") +
  papaja::theme_apa() +
  scale_color_manual(values = COLORS) +
  scale_fill_manual(values = COLORS) +
  scale_y_continuous(breaks = seq(-1, 1.5, by = 0.2)) +
  rt_theme

cd_ACC
```

## 4.3 Combined Plot
```{r}
combined_plot1 <- RT / ACC +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

combined_plot1
```

## 4.4 Cohen's d Combined Plot
```{r}
combined_plot2 <- cd_RT / cd_ACC +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

combined_plot2
```

## 4.5 Save
```{r}
ggsave(here::here("3_Study3&4", "figures", "ACC.png"), plot = ACC, width = 11, height = 7, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "cd_ACC.png"), plot = cd_ACC, width = 14, height = 5, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "combined_plot1.png"), plot = combined_plot1, width = 12, height = 11, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "combined_plot2.png"), plot = combined_plot2, width = 19, height = 11, dpi = 300)
```

---

# Part 5: DDM Parameter Analysis

## 5.1 Load DDM Parameters
```{r}
# Load DDM parameters from processed data
para_emp <- read.csv(here::here("3_Study3&4", "data", "processed", "ddm_params.csv")) %>%
  mutate(Type = "empirical") %>%
  left_join(GROUP_INFO %>% select(new_groupID, Condition), by = c("groupID" = "new_groupID"))
```

## 5.2 Bootstrap v_diff
```{r}
set.seed(42)
v_bootstrap <- data.frame()
for (g in unique(para_emp$groupID)) {
  d <- para_emp %>% filter(groupID == g) %>% pull(v_diff)
  b <- boot::boot(d, function(x, i) mean(x[i]), R = 5000)
  ci <- boot::boot.ci(b, type = "perc")$perc
  v_bootstrap <- bind_rows(v_bootstrap, data.frame(
    groupID = g, mean_v_diff = mean(d), ci_lower = ci[4], ci_upper = ci[5]
  ))
}

v_bootstrap <- v_bootstrap %>% left_join(GROUP_INFO %>% select(new_groupID, Condition), 
                                         by = c("groupID" = "new_groupID"))

# Simulated v_diff
para_sim <- df_sim %>% group_by(groupID, Label) %>% summarise(v = mean(v), a = mean(a), .groups = "drop") %>%
  pivot_wider(id_cols = groupID, names_from = Label, values_from = v) %>%
  mutate(v_diff = self - stranger) %>% left_join(GROUP_INFO %>% select(new_groupID, Condition), 
                                                    by = c("groupID" = "new_groupID"))
```

## 5.3 Bootstrap Plots
```{r}
group_labels <- setNames(GROUP_INFO$Condition, GROUP_INFO$new_groupID)
colors <- RColorBrewer::brewer.pal(8, "RdBu")

bootstrap_vdiff <- ggplot(para_emp, aes(x = factor(groupID), y = v_diff, fill = factor(groupID))) +
  stat_halfeye(adjust = 1, justification = -0.3, .width = 0, point_alpha = 0, alpha = 0.7, scale = 0.6) +
  geom_jitter(aes(color = factor(groupID)), width = 0.1, alpha = 0.1, size = 1.5) +
  geom_crossbar(data = v_bootstrap, aes(y = mean_v_diff, ymin = ci_lower, ymax = ci_upper), 
                width = 0.15, color = "black", alpha = 0.2) +
  geom_point(data = para_sim, aes(x = factor(groupID), y = v_diff), color = "black", shape = 17, size = 4) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 0.8) +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
  scale_x_discrete(labels = group_labels) +
  scale_y_continuous(breaks = seq(-1, 6, by = 1)) +
  labs(x = "Condition", y = "Bootstrap Means") +
  papaja::theme_apa() + rt_theme + theme(legend.position = "none")

bootstrap_vdiff
```

## 5.4 Save
```{r}
ggsave(here::here("3_Study3&4", "figures", "bootstrap_vdiff.png"), plot = bootstrap_vdiff, width = 22, height = 7, dpi = 300)

bruceR::export(para_emp, file = here::here("3_Study3&4", "data", "processed", "ddm_params.csv"))
bruceR::export(v_bootstrap, file = here::here("3_Study3&4", "data", "processed", "ddm_bootstrap.csv"))
```

---

# Part 6: Hierarchical Bootstrap Analysis

## 6.1 Prepare Bootstrap Data
```{r}
# Filter empirical data for bootstrap (exclude group 7 nomask)
emp_bootstrap <- df_emp_match %>%
  filter(!is.na(RT_ms) & groupID != 7) %>% 
  mutate(
    uniqueID = paste(groupID, subjectID, Label, sep = "_"),
    subjID = paste(groupID, subjectID, sep = "_")
  )

# Label colors for plots
label_colors <- c("self" = "#a72126", "stranger" = "#12264f")
```

## 6.2 Bootstrap Functions
```{r}
# Bootstrap Cohen's d for RT
bootstrap_cohens_d_rt <- function(data, R = 5000) {
  self_data <- data$RT_ms[data$Label == "self"]
  stranger_data <- data$RT_ms[data$Label == "stranger"]
  
  if (length(self_data) < 2 | length(stranger_data) < 2) {
    return(list(t0 = NA, t = NA))
  }
  
  boot_fun <- function(d, indices) {
    d_sub <- d[indices, ]
    s <- d_sub$RT_ms[d_sub$Label == "self"]
    st <- d_sub$RT_ms[d_sub$Label == "stranger"]
    if (length(s) < 2 | length(st) < 2) return(NA)
    pooled_sd <- sqrt(((length(s) - 1) * sd(s)^2 + (length(st) - 1) * sd(st)^2) / (length(s) + length(st) - 2))
    (mean(st) - mean(s)) / pooled_sd
  }
  
  boot::boot(data, boot_fun, R = R)
}

# Bootstrap Cohen's d for ACC
bootstrap_cohens_d_acc <- function(data, R = 5000) {
  self_data <- data$Correct[data$Label == "self"]
  stranger_data <- data$Correct[data$Label == "stranger"]
  
  if (length(self_data) < 2 | length(stranger_data) < 2) {
    return(list(t0 = NA, t = NA))
  }
  
  boot_fun <- function(d, indices) {
    d_sub <- d[indices, ]
    s <- d_sub$Correct[d_sub$Label == "self"]
    st <- d_sub$Correct[d_sub$Label == "stranger"]
    if (length(s) < 2 | length(st) < 2) return(NA)
    pooled_sd <- sqrt(((length(s) - 1) * sd(s)^2 + (length(st) - 1) * sd(st)^2) / (length(s) + length(st) - 2))
    (mean(s) - mean(st)) / pooled_sd
  }
  
  boot::boot(data, boot_fun, R = R)
}

# Extract bootstrap results
extract_bootstrap_results <- function(boot_obj, subj_id, prefix) {
  ci <- tryCatch({
    boot::boot.ci(boot_obj, type = "perc")$perc[4:5]
  }, error = function(e) c(NA, NA))
  
  data.frame(
    subjID = subj_id,
    d_mean = boot_obj$t0,
    d_lower = ci[1],
    d_upper = ci[2],
    stringsAsFactors = FALSE
  )
}
```

## 6.3 Run Bootstrap for Each Subject (RT)
```{r}
set.seed(522)

emp_bootstrap_cd_RT <- lapply(split(emp_bootstrap, emp_bootstrap$subjID), function(subj_data) {
  bootstrap_cohens_d_rt(as.data.frame(subj_data), R = 5000)
})
```

## 6.4 Extract RT Bootstrap Results
```{r}
emp_bootstrap_cd_RT_df <- do.call(rbind, lapply(seq_along(emp_bootstrap_cd_RT), function(i) {
  boot_obj <- emp_bootstrap_cd_RT[[i]]
  subj_id <- names(emp_bootstrap_cd_RT)[i]
  extract_bootstrap_results(boot_obj, subj_id, prefix = "mean_RT")
}))

# Split subjID into groupID and subjectID
emp_bootstrap_cd_RT_df <- emp_bootstrap_cd_RT_df %>%
  separate(subjID, into = c("groupID", "subjectID"), sep = "_", remove = FALSE) %>%
  arrange(subjID)
```

## 6.5 Run Bootstrap for Each Subject (ACC)
```{r}
set.seed(522)

emp_bootstrap_cd_ACC <- lapply(split(emp_bootstrap, emp_bootstrap$subjID), function(subj_data) {
  bootstrap_cohens_d_acc(as.data.frame(subj_data), R = 5000)
})
```

## 6.6 Extract ACC Bootstrap Results
```{r}
emp_bootstrap_cd_ACC_df <- do.call(rbind, lapply(seq_along(emp_bootstrap_cd_ACC), function(i) {
  boot_obj <- emp_bootstrap_cd_ACC[[i]]
  subj_id <- names(emp_bootstrap_cd_ACC)[i]
  extract_bootstrap_results(boot_obj, subj_id, prefix = "mean_ACC")
}))

# Split subjID into groupID and subjectID
emp_bootstrap_cd_ACC_df <- emp_bootstrap_cd_ACC_df %>%
  separate(subjID, into = c("groupID", "subjectID"), sep = "_", remove = FALSE) %>%
  arrange(subjID)
```

## 6.7 Group-Level Hierarchical Bootstrap CI (RT)
```{r}
group_ids <- unique(emp_bootstrap_cd_RT_df$groupID)

group_bootstrap_RT <- lapply(group_ids, function(gid) {
  group_data <- emp_bootstrap_cd_RT_df %>% filter(groupID == gid)
  
  # Filter out subjects with NA bootstrap values
  valid_subjects <- group_data %>% filter(!is.na(d_mean))
  
  if (nrow(valid_subjects) == 0) {
    return(data.frame(
      groupID = gid,
      group_d_mean = NA,
      group_d_lower = NA,
      group_d_upper = NA
    ))
  }
  
  subject_split <- split(valid_subjects$d_mean, valid_subjects$subjectID)
  n_boot <- length(subject_split[[1]])
  
  group_boot_d <- replicate(n_boot, {
    sampled_d <- sapply(subject_split, function(d_vec) sample(d_vec, 1))
    mean(sampled_d, na.rm = TRUE)
  })
  
  data.frame(
    groupID = gid,
    group_d_mean = mean(group_boot_d, na.rm = TRUE),
    group_d_lower = quantile(group_boot_d, 0.025, na.rm = TRUE),
    group_d_upper = quantile(group_boot_d, 0.975, na.rm = TRUE)
  )
})

group_bootstrap_RT_df <- bind_rows(group_bootstrap_RT)
```

## 6.8 Group-Level Hierarchical Bootstrap CI (ACC)
```{r}
group_bootstrap_ACC <- lapply(group_ids, function(gid) {
  group_data <- emp_bootstrap_cd_ACC_df %>% filter(groupID == gid)
  
  # Filter out subjects with NA bootstrap values
  valid_subjects <- group_data %>% filter(!is.na(d_mean))
  
  if (nrow(valid_subjects) == 0) {
    return(data.frame(
      groupID = gid,
      group_d_mean = NA,
      group_d_lower = NA,
      group_d_upper = NA
    ))
  }
  
  subject_split <- split(valid_subjects$d_mean, valid_subjects$subjectID)
  n_boot <- length(subject_split[[1]])
  
  group_boot_d <- replicate(n_boot, {
    sampled_d <- sapply(subject_split, function(d_vec) sample(d_vec, 1))
    mean(sampled_d, na.rm = TRUE)
  })
  
  data.frame(
    groupID = gid,
    group_d_mean = mean(group_boot_d, na.rm = TRUE),
    group_d_lower = quantile(group_boot_d, 0.025, na.rm = TRUE),
    group_d_upper = quantile(group_boot_d, 0.975, na.rm = TRUE)
  )
})

group_bootstrap_ACC_df <- bind_rows(group_bootstrap_ACC)
```

## 6.9 Summary Bootstrap Statistics (RT)
```{r}
# Print summary statistics
cat("=== RT Bootstrap Summary ===\n")
print(head(emp_bootstrap_cd_RT_df))
cat("\n=== Group-Level RT Bootstrap CI ===\n")
print(group_bootstrap_RT_df)
```

## 6.10 Summary Bootstrap Statistics (ACC)
```{r}
cat("=== ACC Bootstrap Summary ===\n")
print(head(emp_bootstrap_cd_ACC_df))
cat("\n=== Group-Level ACC Bootstrap CI ===\n")
print(group_bootstrap_ACC_df)
```

## 6.11 Save Bootstrap Results
```{r}
bruceR::export(emp_bootstrap_cd_RT_df, file = here::here("3_Study3&4", "data", "processed", "bootstrap_cd_RT.csv"))
bruceR::export(emp_bootstrap_cd_ACC_df, file = here::here("3_Study3&4", "data", "processed", "bootstrap_cd_ACC.csv"))
bruceR::export(group_bootstrap_RT_df, file = here::here("3_Study3&4", "data", "processed", "group_bootstrap_RT.csv"))
bruceR::export(group_bootstrap_ACC_df, file = here::here("3_Study3&4", "data", "processed", "group_bootstrap_ACC.csv"))
```

---

# Part 7: Ridge Plots

## 7.1 Prepare Ridge Data
```{r}
# Prepare data for ridge plots
df_emp_individual_wide <- df_individual_wide %>%
  filter(Type == "empirical" & groupID != 7) %>%
  unite(subjID, groupID, subjectID, sep = "_", remove = FALSE) %>%
  select(subjID, groupID, subjectID, cohen_d_RT, cohen_d_ACC)

df_emp_group_wide <- df_group_wide %>%
  filter(Type == "empirical" & groupID != 7) %>%
  select(groupID, cohen_d_RT, cohen_d_ACC)

# Prepare RT bootstrap long format
emp_bootstrap_RT_long <- emp_bootstrap_cd_RT_df %>%
  select(subjID, groupID, subjectID) %>%
  mutate(label = "RT") %>%
  left_join(df_emp_match %>% 
              filter(Type == "empirical") %>%
              group_by(groupID, subjectID, Label) %>%
              summarise(mean_RT = mean(RT_ms, na.rm = TRUE), .groups = "drop") %>%
              mutate(subjID = paste(groupID, subjectID, sep = "_")),
            by = "subjID")

# Prepare ACC bootstrap long format  
emp_bootstrap_ACC_long <- emp_bootstrap_cd_ACC_df %>%
  select(subjID, groupID, subjectID) %>%
  mutate(label = "ACC") %>%
  left_join(df_emp_match %>%
              filter(Type == "empirical") %>%
              group_by(groupID, subjectID, Label) %>%
              summarise(mean_ACC = mean(Correct, na.rm = TRUE), .groups = "drop") %>%
              mutate(subjID = paste(groupID, subjectID, sep = "_")),
            by = "subjID")
```

## 7.2 Ridge Plot: Cohen's d RT
```{r}
# Filter valid data for ridge plot
ridge_data_RT <- emp_bootstrap_cd_RT_df %>% 
  filter(!is.na(d_mean)) %>%
  mutate(groupID = as.factor(groupID))

ridge_group_RT <- group_bootstrap_RT_df %>%
  filter(!is.na(group_d_mean)) %>%
  mutate(groupID = as.factor(groupID))

Ridge_cd_RT <- ggplot() +
  geom_density_ridges(
    data = ridge_data_RT, 
    aes(x = d_mean, y = groupID),
    scale = 0.8,
    fill = "#594c57",
    alpha = 0.6,
    color = NA,
    bandwidth = 0.1
  ) +
  geom_segment(
    data = ridge_group_RT,
    aes(x = group_d_lower, xend = group_d_upper, y = as.factor(groupID), yend = as.factor(groupID)),
    color = "black",
    size = 1.2
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  scale_x_continuous(
    limits = c(-1, 2),
    breaks = seq(-1.5, 2, by = 0.5)
  ) +
  labs(
    x = "Cohen's d RT",
    y = "Group"
  ) +
  papaja::theme_apa() +
  rt_theme

Ridge_cd_RT
```

## 7.3 Ridge Plot: Cohen's d ACC
```{r}
# Filter valid data for ridge plot
ridge_data_ACC <- emp_bootstrap_cd_ACC_df %>% 
  filter(!is.na(d_mean)) %>%
  mutate(groupID = as.factor(groupID))

ridge_group_ACC <- group_bootstrap_ACC_df %>%
  filter(!is.na(group_d_mean)) %>%
  mutate(groupID = as.factor(groupID))

Ridge_cd_ACC <- ggplot() +
  geom_density_ridges(
    data = ridge_data_ACC, 
    aes(x = d_mean, y = groupID),
    scale = 0.8,
    fill = "#594c57",
    alpha = 0.6,
    color = NA,
    bandwidth = 0.1
  ) +
  geom_segment(
    data = ridge_group_ACC,
    aes(x = group_d_lower, xend = group_d_upper, y = as.factor(groupID), yend = as.factor(groupID)),
    color = "black",
    size = 1.2
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  scale_x_continuous(
    limits = c(-1, 2),
    breaks = seq(-1.5, 2, by = 0.5)
  ) +
  labs(
    x = "Cohen's d ACC",
    y = "Group"
  ) +
  papaja::theme_apa() +
  rt_theme

Ridge_cd_ACC
```

## 7.4 Combined Ridge Plot
```{r}
Ridge_cd_RT_clean <- Ridge_cd_RT +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

Ridge_cd_ACC_clean <- Ridge_cd_ACC +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

Combined_Ridge <- Ridge_cd_RT_clean + Ridge_cd_ACC_clean +
  plot_layout(ncol = 2, guides = "collect") & 
  theme(legend.position = "bottom")

Combined_Ridge
```

## 7.5 Save Ridge Plots
```{r}
ggsave(here::here("3_Study3&4", "figures", "Ridge_cd_RT.png"), plot = Ridge_cd_RT, width = 14, height = 10, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "Ridge_cd_ACC.png"), plot = Ridge_cd_ACC, width = 14, height = 10, dpi = 300)
ggsave(here::here("3_Study3&4", "figures", "Ridge_combined.png"), plot = Combined_Ridge, width = 22, height = 10, dpi = 300)
```

---

Analysis complete!

---

*`r Sys.Date()`*
